Examples of Customization

### 2016-09-26 writing/custom_examples.Rmd
Add customization examples to vignette

```{r}
binary_exposure(n=5, p = .2, y = .1, trend = "custom", custom_func = sintrend)
plot(binary_exposure(n=400, p = .2, y = .1, trend = "custom", custom_func = sintrend))

>>>>

```{r}
binary_exposure(n=5, p = .2, y = .1, trend = "custom", custom_func = sintrend)
plot(binary_exposure(n=400, p = .2, y = .1, amp = .01, trend = "custom", custom_func = sintrend))
